Sequence data processing

### 2022-06-24 R/07-process-community.Rmd
add seqs to output community data file

# Check if taxa names match between the otu and taxa tables
sum(colnames(seqtab.nochim) != rownames(taxa))
# They match if = 0

colnames(seqtab.nochim) <- paste0("ASV", seq(ncol(seqtab.nochim)))
rownames(seqtab.nochim) <- metadata$sample
rownames(taxa) <- colnames(seqtab.nochim)

@@

# Sequence Depth Distribution + Sample Composition

@@

@@

>>>>

# Check if taxa names match between the otu and taxa tables
sum(colnames(seqtab.nochim) != rownames(taxa))
# They match if = 0 
seqs <- tibble(asv = paste0("ASV", seq(ncol(seqtab.nochim))),
               seq = colnames(seqtab.nochim))
colnames(seqtab.nochim) <- paste0("ASV", seq(ncol(seqtab.nochim)))
rownames(seqtab.nochim) <- metadata$sample
rownames(taxa) <- colnames(seqtab.nochim)

@@

# Sequence Depth Distribution

@@

# Beta Diversity all samples

@@

full_data <-
  full_data %>% 
  left_join(seqs, by = "asv")
